Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-13 ms.tex
I discovered that the MORIS photometry was having the SpeX error bar scaling but should not. Now I think it adds a potentially useful upper limit to the short wavelength part of the spectrum.

I made a time series of my photometry to see if it would help with the spectrum fit.

The SNR is so low that's it hard to see any clear pattern.
The photometry adds very little to the spectrum, as seen in Figure \ref{fig:morisPhotometryAndSpec}.

\begin{figure*}[!t]
\centering
\subfloat[MORIS $i$ Band Photometry for \shb]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_moris_tser_best_fit.pdf}
	\label{fig:morisTSerBestFit}
	}
\subfloat[Amplitude spectrum for \shb\ when adding MORIS photometry]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_a1_spec_w_moris.pdf}
	\label{fig:spectrum1821WMoris}
	}
	\caption{MORIS photometry does not significantly improve the constraints on the spectrum.}
	\label{fig:morisPhotometryAndSpec}
\end{figure*}

>>>>

I made a time series of the MORIS $i$ band photometry to see if it would help with the spectrum fit.
The SNR is so low that's it hard to see any clear pattern.
However, the photometry can put upper limits to the spectrum, as seen in Figure \ref{fig:spectrum1821WMoris}.

\begin{figure*}[!t]
\centering
\subfloat[MORIS $i$ Band Photometry for \shb]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_moris_tser_best_fit.pdf}
	\label{fig:morisTSerBestFit}
	}
\subfloat[Amplitude spectrum for \shb\ when adding MORIS photometry]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_a1_spec_w_moris.pdf}
	\label{fig:spectrum1821WMoris}
	}
	\caption{MORIS photometry can put an upper limit on the short wavelength end of the spectrum spectrum.}
	\label{fig:morisPhotometryAndSpec}
\end{figure*}
